true

### 2020-04-27 analysis/robinson2020.Rmd
getting travis working

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."))
  unlink(here::here("analysis/data/derived_data/."))
}
```

>>>>

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."))
  # unlink(here::here("analysis/data/derived_data/."))
}
```
